A simple R markdown example

### 2020-05-19 R/rmarkdown.Rmd
updated rmarkdown example (Fig2/Fig3), possibly broken now

---
title: "A simple RMarkdown Example"
author: "Aaron Peikert & Andreas M. Brandmaier"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

```{r setup}
library("knitr")
library("papaja")
```

# Silly Heading

```{r t-test}
data("sleep")
result <- t.test(extra ~ group, data = sleep)
```

This is an example on students' sleep data taken from `help(t.test)`.

`r apa_print.htest(result)$full_result`

I can now assert that what I *believe* to be true
--- that there is a difference in means between the groups ---
is `r ifelse(result$p.value > .025, "**not**", "")` supported by data.

>>>>

---
#title: "\\vspace{-1em}A simple R markdown example\\vspace{-1em}"
#author: "Aaron Peikert & Andreas M. Brandmaier"
output: pdf_document
papersize: "a6"
fontsize: 9pt
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

### Dynamic Document Demonstration

```{r setup, echo=FALSE}
library("knitr")
library("papaja")
```

This is a simple analysis of the `sleep` dataset (Student, 1908) taken from `help(t.test)`.

```{r t-test}
data("sleep")
result <- t.test(extra ~ group, data = sleep, paired = TRUE)
```

The difference in means of hours slept between the groups 
was `r ifelse(result$p.value >= .05, "**not**", "")` 
significantly different from zero (`r apa_print.htest(result)$full_result`).
